\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2010-11-21 doc/USER_MANUAL/manual_SPECFEM3D.tex
final version of the new covers (in Adobe Illustrator and in PDF formats); final version of the list of authors

% figures
\usepackage[dvips]{epsfig}

@@

\begin{document}
\thispagestyle{empty}\textbf{}%
\begin{figure}[H]
\noindent \includegraphics[width=0.75\paperwidth]{figures/specfem_3d-cover.pdf}
\end{figure}

\title{\textbf{SPECFEM3D}\\
\textbf{User Manual}}

\author{$\copyright$ Princeton University (USA) and\\
University of Pau / CNRS / INRIA (France)\\
Version 2.0.0 \\
"Sesame"
}

@@

\section*{Authors}
The SPECFEM3D package was first developed by Dimitri Komatitsch and Jeroen Tromp at Harvard University, then Caltech and Princeton, USA, starting in 1998, based in part on earlier work by Dimitri Komatitsch and Jean-Pierre Vilotte at IPG in Paris, France from 1994 to 1997. \\

Since then it has been developed and maintained by a development team: in alphabetical order,
Piero Basini,
Ebru Bozdag,
Emanuele Casarotti,
Min Chen,
Hom Nath Gharti,
Vala Hj\"orleifsd\'ottir,
Emiljana Jorgji,
Sue Kientz,
Dimitri Komatitsch,
Jes\'us Labarta,
Nicolas Le Goff,
Pieyre Le Loher,
Qinya Liu,
Yang Luo,
Alessia Maggi,
Federica Magnoni,
Roland Martin,
Dennis McRitchie,
David Mich\'ea,
Tarje Nissen-Meyer,
Daniel Peter,
Brian Savage,
Leif Strand,
Carl Tape,
Jeroen Tromp.\\

\toall{add full list of developers here and update the AUTHORS file accordingly} \\

The cover graphic of the manual was created
by Santiago Lombeyda from Caltech's Center for Advanced Computing Research (CACR) \url{http://www.cacr.caltech.edu}.
Sue Kientz assembled the manual.\\

\toall{We should also update the Adobe Illustrator / PDF cover page as well at some point} \\

@@

The software package SPECFEM3D simulates seismic
wave propagation at the local or regional scale
based upon the spectral-element method (SEM).
The SEM is a continuous Galerkin technique, which can easily be made discontinous \citep{BeMaPa94,KoWoHu02,ChCaVi03,Kop06,WiStBuGh10}; it is then a particular case of the discontinuous Galerkin technique \citep{ReHi73,FaRi99,HuHuRa99,CoKaSh00,GiHeWa02,RiWh03,MoRi05,GrScSc06,BeLaPi06,DuKa06,DeSeWh08,WiStBuGh10,DeSe10,EtChViGl10}, with optimized efficiency because of its tensorized basis functions.
In particular, it can accurately handle very distorted mesh elements \citep{OlSe11}.
Note that in most geological models in the context of seismic wave propagation studies
(except for fault dynamic rupture studies)
a discontinous mesh is not needed because material property contrasts are not drastic and thus a continuous formulation is sufficient. For a detailed introduction to the SEM as applied to regional
seismic wave propagation, please consult \citet{KoVi98,KoTr99,ChKoViCaVaFe07,TrKoLi08} and
in particular \citet{KoLiTrSuStSh04}.

Effects due to lateral variations in compressional-wave speed, shear-wave
speed, density, a 3D crustal model, topography and bathymetry are
included. The package can accommodate
full 21-parameter anisotropy (see~\citet{ChTr07}) as well as lateral
variations in attenuation \citep{SaKoTr10}. Adjoint capabilities and finite-frequency
kernel simulations are included \citep{LiTr06,TrKoLi08,FiIgBuKe09}.

%The SPECFEM3D package was first developed by Dimitri Komatitsch and Jeroen Tromp at Harvard University, then Caltech and Princeton, USA, starting in 1998, based in part on earlier work by Dimitri Komatitsch and Jean-Pierre Vilotte at IPG in Paris, France from 1994 to 1997. Since then it has been developed and maintained by a development team: in alphabetical order,
%Emanuele Casarotti,
%Min Chen,
%Vala Hj\"orleifsd\'ottir,
%Emiljana Jorgji,
%Sue Kientz,
%Dimitri Komatitsch,
%Qinya Liu,
%Yang Luo,
%Nicolas Le Goff,
%Pieyre Le Loher,
%Alessia Maggi,
%Roland Martin,
%Dennis McRitchie,
%David Mich\'ea,
%Daniel Peter,
%Brian Savage,
%Leif Strand,
%Carl Tape,
%Jeroen Tromp
%\toall{add full list of developers here and update the AUTHORS file accordingly}.

%\toall{We should also update the Adobe Illustrator / PDF cover page as well at some point}

@@

%\cite{TrKoLi08,VaCaSaKoVi99,LeChLiKoHuTr08,LeChKoHuTr09,LeKoHuTr09,KoMiEr09,KoErGoMi10,KoGoErMi10,WiKoScTr04,KoLiTrSuStSh04,ChKoViCaVaFe07,MaKoDi09,KoViCh10,CaKoLaTiMiLeSnTr08,TrKoHjLiZhPeBoMcFrTrHu10,KoRiTr02,KoTr02a,KoTr02b,KoTr99} or \cite{KoVi98}.

%If you work on geophysical applications, you may be interested in citing some of these application articles as well, among others: \cite{WiKoScTr04,JiTsKoTr05,KrJiKoTr06a,KrJiKoTr06b,LeChLiKoHuTr08,LeChKoHuTr09,LeKoHuTr09,ChFaKo04,FaChKo04,RiRiKoTrHe02,GoAmTaCaSmSaMaKo09,TrKo00,SaKoTr10}.

>>>>

@@

\begin{document}
\begin{center}
\thispagestyle{empty}%
\vspace*{-1.8truecm}
\noindent\makebox[\textwidth]{%
\noindent\includegraphics[width=0.83\paperwidth]{figures/specfem_3d-cover.pdf}
}
\end{center}
%
\title{\textbf{SPECFEM3D}\\
\textbf{User Manual}}

\author{$\copyright$ Princeton University (USA) and\\
University of Pau / CNRS / INRIA (France)\\
Version 2.0.0 \\
"Sesame"}

\date{\noindent \today}

@@

\section*{Authors}
The SPECFEM3D package was first developed by Dimitri Komatitsch and Jeroen Tromp at Harvard University and Caltech, USA, starting in 1998, based in part on earlier work by Dimitri Komatitsch and Jean-Pierre Vilotte at Institut de Physique du Globe (IPGP) in Paris, France from 1994 to 1997.\\

Since then it has been developed and maintained by a development team: in alphabetical order,
Piero Basini,
C\'eline Blitz,
Ebru Bozdag,
Emanuele Casarotti,
Min Chen,
Vala Hj\"orleifsd\'ottir,
Emiljana Jorgji,
Sue Kientz,
Dimitri Komatitsch,
Jes\'us Labarta,
Nicolas Le Goff,
Pieyre Le Loher,
Qinya Liu,
Yang Luo,
Alessia Maggi,
Federica Magnoni,
Roland Martin,
Dennis McRitchie,
David Mich\'ea,
Hom Nath Gharti,
Tarje Nissen-Meyer,
Daniel Peter,
Brian Savage,
Leif Strand,
Carl Tape,
Jeroen Tromp.\\
% \toall{add full list of developers here and update the AUTHORS file accordingly}

The cover graphic of the manual was created
by Santiago Lombeyda from Caltech's Center for Advanced Computing Research (CACR) \url{http://www.cacr.caltech.edu}.\\

@@

The software package SPECFEM3D simulates seismic
wave propagation at the local or regional scale
based upon the spectral-element method (SEM).
The SEM is a continuous Galerkin technique, which can easily be made discontinous \citep{BeMaPa94,KoWoHu02,ChCaVi03,Kop06,WiStBuGh10}; it is then a particular case of the discontinuous Galerkin technique \citep{ReHi73,FaRi99,HuHuRa99,CoKaSh00,GiHeWa02,RiWh03,MoRi05,GrScSc06,BeLaPi06,DuKa06,DeSeWh08,WiStBuGh10,DeSe10,EtChViGl10}, with optimized efficiency because of its tensorized basis functions.
In particular, it can accurately handle very distorted mesh elements \citep{OlSe11}.
Note that in most geological models in the context of seismic wave propagation studies
(except for fault dynamic rupture studies)
a discontinous mesh is not needed because material property contrasts are not drastic and thus a continuous formulation is sufficient. For a detailed introduction to the SEM as applied to regional
seismic wave propagation, please consult \citet{KoVi98,KoTr99,ChKoViCaVaFe07,TrKoLi08} and
in particular \citet{KoLiTrSuStSh04}.
A detailed theoretical analysis of the dispersion
and stability properties of the SEM is available in \citet{Coh02}, \citet{DeSe07} and \citet{SeOl07}.

Effects due to lateral variations in compressional-wave speed, shear-wave
speed, density, a 3D crustal model, topography and bathymetry are
included. The package can accommodate
full 21-parameter anisotropy (see~\citet{ChTr07}) as well as lateral
variations in attenuation \citep{SaKoTr10}. Adjoint capabilities and finite-frequency
kernel simulations are included \citep{LiTr06,TrKoLi08,FiIgBuKe09,ViOp09}.

@@
